Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis

### 2017-12-06 paper.tex
Added a page of Introduction, some references, and some Acknowledgements

There will be a whole bunch of papers cited here...

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\acknowledgments
George Bryan, Jeff Kepert, and Rob Fovell.

>>>>

Perhaps introduce upper-tropospheric static stability and its relationship to the diurnal cycle before going into Patricia? Include references to Dunion, Navarro, and O'Neill here.

After undergoing a remarkably rapid intensification (RI), Hurricane Patricia (2015) set a new record as the strongest tropical cyclone (TC) ever observed in the Western Hemisphere (\citeauthor{Kimberlainetal2016} \citeyear{Kimberlainetal2016}; \citeauthor{Rogersetal2017} \citeyear{Rogersetal2017}).
High-altitude dropsonde observations taken by the Tropical Cyclone Intensity (TCI) Experiment captured this RI in unprecedented detail \citep{DoyleTCI}.
These observations revealed remarkable changes in the structure of the cold-point tropopause and upper-level static stability as the storm intensified \citep{Duran+Molinari2018}.
At tropical storm intensity, shortly before RI commenced, a strong inversion layer existed just above Patricia's cold-point tropopause, which was located near 17.2 km.
During the first half of the RI period, this inversion layer weakened throughout Patricia's inner core, with the weakening most pronounced over the developing eye.
By the time the storm reached its maximum intensity, the inversion layer over the eye had disappeared almost completely, which was accompanied by an increase in the tropopause height to a level at or above the highest-available dropsonde data point (18.3 km) at two locations.
Meanwhile over the eyewall region, the static stability re-strengthened and the tropopause was limited to a level at or below 17.5 km.
The mechanisms that led to these changes in upper-level static stability and tropopause height are the subject of the current paper.

More recently, \cite{Dunionetal2014} documented a periodic oscillation of infrared brightness temperature in hurricanes, which they call the "TC diurnal pulse."
There will be a whole bunch of papers cited here...

At some point (probably in the Discussion) mention the possible importance of static stability asymmetries, in the context of the Dunion diurnal pulse

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\acknowledgments
We are indebted to Dr. George Bryan for his continued development and support of Cloud Model 1.
We also thank Drs. Jeffrey Kepert, Robert Fovell, and Erika Navarro for fruitful conversations related to this work.
ADD GRANT NUMBER
